%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineering Intern - YouTube Main Web App} % Job title
{Google} % Organization
{Mountain View, California} % Location
{May 2016 - Aug. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Incorporated Lighthouse, an open
source developer's tool created by the Chrome team, into the YouTube front-end
testing suite as a continuous integration tool to prevent performance
regression.}
\item {Extensively communicated and coordinated between
different teams from various offices in order to integrate the necessary tools
together to create an easy to use tool with a customizable API.}
\item {Implemented new elements on the YouTube main desktop app
and contributing to the Lighthouse open source project.}
\item {Presented at an internal Google conference, showcasing the various use
cases and advantages of using Lighthouse inside the Google codebase.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Full Stack Engineering Intern} % Job title
{Polis Politics} % Organization
{Boston, MA} % Location
{July 2015 - May 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Componsed dynamic data visualizations of voter support and turnout in
designated precincts using campaign canvassing data and the Google Maps API.}
\item {Set up the necessary back-end database infrastructure and API endpoints
to support the client-side map visualizations.}
\item {Participated in local campaign canvassing events to build better user
stories and strengthen relationships with consumers.}
\item {Used Es6 JavaScript, React, and Node.JS extensively.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Student SQL Programmer} % Job title
{BU Alumni Association} % Organization
{Boston, MA} % Location
{Sep. 2015 - Feb. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked with a full-time programmer to collect, aggregate, and analyze
data for the Boston University Alumni Association.}
\item {Built custom SQL queries, stored procedures, and accompanying models on
the consumer relationship manager's front-end to support the BU Alumni
Association with data creation and visualization.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{MET CS201, Introduction to Programming} % Job title
{BU Course Assistant} % Organization
{Boston, MA} % Location
{Spring and Summer Semesters, 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Graded assignments and held office hours to assist struggling students
get a better understanding of the course and its topics.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
